%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{xcolor}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Han Gao} % Your name
\address{Last update \today} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+1)3142553782 \\ hgao1@seas.harvard.edu} % Your phone number and
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf University of Notre Dame, South Bend} \hfill {\em June 2018 - June 2023} 
\\ Doctor of Philosophy, Aerospace and Mechanical Engineering.\\
Advisor and mentor: \textit{Jian-Xun Wang}\\
%Also closely trained by: \textit{Matthew Zahr}\\
{\bf Washington University in St. Louis, St. Louis} \hfill {\em August 2016 - May 2018} 
\\ Master of Science, Mechanical Engineering.\\
Advisor and mentor: \textit{Ramesh K. Agarwal}\\
{\bf Shanghai University of Electric Power, Shanghai} \hfill {\em September 2012 - June 2016} 
\\ Bachelor of Engineering, Mechanical Engineering.\\
\end{rSection}

\begin{rSection}{Academic Positions}
\textbf{Postdoctoral Fellow}, \hfill{\em September 2023 - Now}\\
Mentor: \textit{Petros Koumoutsakos}
\\John A. Paulson School of Engineering and Applied Sciences, Harvard University.\\	
\textbf{Research Scientist (Internship)}, \hfill{\em June 2022 - October 2022} 
\\Google Research.\\
\textbf{Research \& Teaching Assistant}, \hfill{\em June 2018 - June 2023}
\\Department of Aerospace and Mechanical Engineering, University of Notre Dame.\\
\textbf{Teaching Assistant}, \hfill {\em June 2017 - May 2018}
\\Department of Mechanical Engineering and Material Science, Washington University in St. Louis.
\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Award}


{\bf Student Travel Award for the SIAM Conference on Uncertainty Quantification (UQ22),} 2022 SIAM-UQ \hfill {\em 2022, Atalanta}\\
{\bf Registration award to the 2020 ASME IMECE,} 2020 IMECE \hfill {\em 2020, Virtual event}\\
{\bf Outstanding Graduate Student Teacher Award,} ND Learning Kaneb Center for Teaching Excellence and The Graduate School \hfill {\em 2020, South Bend}\\
{\bf Third Place Award}, AIAA Region V Student Conference (Graduate group). \hfill {\em 2018, St.Louis}\\
{\bf Top Grade Award}, National Physics Contest for College Students. \hfill {\em 2013, Shanghai}
\end{rSection}




%\begin{rSection}{Research Experience}
%\item 6+ years of experience in machine learning, graphics, computer vision, with combination of: finite element methods, computational mechanics, advanced optimization techniques
%\item 7+ years of experience with numerical simulations of fluid dynamics (Finite volume/element/difference methods)
%\item 7+ years of experience with mesh processing involving complex geometries
%\item 7+ years of experience with programming
%\item 7+ years of hands-on experience with open-source deep-learning frameworks 
%\end{rSection}








%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Thesis}
\item \textbf{Gao, H}. (2023). Scientific Deep Learning for Forward and Inverse Modeling of Spatiotemporal Physics (Doctoral dissertation, University Of Notre Dame).	
\item \textbf{Gao, Han}. ``Numerical Simulations and Studies on Round Jet Impingement, Twin Jet Impingement and Helicopter Rotor Blades Ground Effect." (Master thesis,  Washington University in St. Louis, 2018).
\end{rSection}

\begin{rSection}{Peer-reviewed Journal \& Peer-reviewed Conference Paper}
\item Sun L, Han X, \textbf{Gao H}, et al. Unifying Predictions of Deterministic and Stochastic Physics in Mesh-reduced Space with Sequential Flow Generative Model[C] Thirty-seventh Conference on Neural Information Processing Systems. 2023.	
\item \textbf{Han Gao, Xu Han, Jiaoyang Huang}, Jian-Xun Wang, and Li-Ping Liu. "PatchGT: Transformer over Non-trainable Clusters for Learning Graph Representations" Proceedings of the First Learning on Graphs Conference (LoG 2022). (equal contribution)
\item \textbf{Xu Han, Han Gao, Tobias Pffaf}, Jian-Xun Wang, and Li-Ping Liu. "Predicting Physics in Mesh-reduced Space with Temporal Attention." The Tenth International Conference on Learning Representations ICLR 2022. (equal contribution)

\item \textbf{Gao, Han}, Matthew J. Zahr, and Jian-Xun Wang. "Physics-informed graph neural Galerkin networks: A unified framework for solving PDE-governed forward and inverse problems." CMAME (2021).


\item \textbf{Gao, Han}, Luning Sun, and Jian-Xun Wang. ''Super-resolution and denoising of fluid flow using physics-informed convolutional neural networks without high-resolution labels." Physics of Fluids (Accepted, \textbf{Promoted as editor's pick}).

\item \textbf{Gao, Han}, and Jian-Xun Wang.``A Bi-fidelity ensemble kalman method for PDE-constrained inverse problems in computational mechanics." Computational Mechanics (2021): 1-17.\\

\item \textbf{Gao, Han}, Luning Sun, and Jian-Xun Wang. ``PhyGeoNet: Physics-informed geometry-adaptive convolutional neural networks for solving parameterized steady-state PDEs on irregular domain." Journal of Computational Physics 428 (2021): 110079.

\item \textbf{Gao, Han}, Jian-Xun Wang, and Matthew J. Zahr. ``Non-intrusive model reduction of large-scale, nonlinear dynamical systems using deep learning." Physica D: Nonlinear Phenomena 412 (2020): 132614.\\

\item \textbf{Gao, Han}, Xueyu Zhu, and Jian-Xun Wang. ``A Bi-fidelity Surrogate Modeling Approach for Uncertainty Propagation in Three-Dimensional Hemodynamic Simulations." Computer Methods in Applied Mechanics and Engineering 366, 113047.\\

\item \textbf{Gao, Han}, Quanzhong Liu, Qiulin Qu, and Ramesh K. Agarwal. ``Study of Round Jet Impingement in Proximity of Ground and Water Surface." Journal of Aircraft (2019): 1-12.\\

\item L. Guo and S. Ye and J. Han and H. Zheng and \textbf{H. Gao} and D. Z. Chen and J.-X. Wang and C. Wang. ``{SSR-VFD}: Spatial Super-Resolution for Vector Field Data Analysis and Visualization", 2020 IEEE Pacific Visualization Symposium (PacificVis), 71-80.\\

\item  L. Sun, \textbf{Gao, Han}, S. Pan et al., ``Surrogate modeling for fluid flows based on physics-constrained deep learning without simulation data", Computer Methods in Applied Mechanics and Engineering (2019) 112732, https://doi.org/10.1016/j.cma.2019.112732
\end{rSection}

\begin{rSection}{Submitted Manuscript} 
%\textbf{Han Gao}, Xu Han, Tobias Pffaf, Jian-Xun Wang, and Li-Ping Liu. ``Graph neural network with temporal attention for learning mesh-based spatiotemporal physics" 

\item \textbf{Gao, H}., Han, X., Fan, X., Sun, L., Liu, L. P., Duan, L., \& Wang, J. X. (2023). Bayesian Conditional Diffusion Models for Versatile Spatiotemporal Turbulence Generation. arXiv preprint arXiv:2311.07896.

\item \textbf{Gao, H}., \& Zahr, M. J. (2023). An adaptive model reduction method leveraging locally supported basis functions. arXiv preprint arXiv:2310.05379.

\item Wang R, \textbf{Gao, H}, Walters R, Smidt TE. Relaxed Octahedral Group Convolution for Learning Symmetry Breaking in 3D Physical Systems. arXiv preprint arXiv:2310.02299. 2023 Oct 3.
\end{rSection}

\begin{rSection}{Conference Papers (Refereed)}

\item \textbf{Han Gao}, Quanzhong Liu, Qiulin Qu, and Ramesh K. Agarwal. ``Numerical Study of Round Jet Impingement in Proximity of Ground and a Water Surface." In 2018 Fluid Dynamics Conference, p. 4257. 2018.

\item \textbf{Han Gao}, and Ramesh K. Agarwal. ``Numerical Study of a Hovering Helicopter Rotor Blade in Ground Effect." In AIAA Scitech 2019 Forum, p. 1099. 2019.

\item \textbf{Han Gao}, Xu Han, Quanzhong Liu, and Ramesh K. Agarwal. ''CFD Simulations of Two Rectangular Water Jets Impinging on a Water Pool." In 2018 Fluid Dynamics Conference, p. 4038. 2018.

\item Liu, Quanzhong, Lujia Gong, \textbf{Han Gao}, and Ramesh K. Agarwal. "Numerical Investigation of Cavitation Characteristics of a Liquid Oxygen Turbo Pump." In 2018 Fluid Dynamics Conference, p. 3222. 2018.

\item Zhang, Xiang, Ramesh K. Agarwal, \textbf{Han Gao}, and Ling Zhou. ``Numerical Investigation of a Submerged Water Jet Impinging at Various Angles on Ground." In AIAA Scitech 2020 Forum, p. 2038. 2020.

\item Zhang, Xiang, Ramesh K. Agarwal, \textbf{Han Gao} and Ling Zhou. ``Numerical Simulation of Fountain formation due to Twin-Jet impingement on Ground." In AIAA Aviation 2019 Forum, p. 3643. 2019.
\end{rSection}

\begin{rSection}{Talk}
\item (\textbf{\color{red}Abstract \& Talk}) Jian-Xun Wang, Xinyang Liu, \textbf{Han Gao} ``Physics-informed model-based deep reinforcement learning for dynamic flow control" 74th Annual Meeting of the APS Division of Fluid Dynamics. 

\item (\textbf{\color{red}Abstract \& Talk}) J.-X. Wang, \textbf{Han Gao}, L. Sun, ``Physics-informed discretization-based learning: a unified framework for solving PDE-constrained forward and inverse problems'' 16th U.S. National Congress on Computational Mechanics (USNCCM16).

\item (\textbf{\color{red}Abstract \& Talk}) \textbf{Gao, Han} and Matthew J. Zahr. ``Parametrically Robust Model Reduction via Enrichment with Locally Supported Basis Functions" 16th U.S. National Congress on Computational Mechanics (USNCCM16). 

\item (\textbf{\color{red}Abstract}) Jianxun Wang, \textbf{Gao, Han}.``Physics-Informed Discretization-Based Learning: a Unified Framework for Solving PDE-Constrained Forward and Inverse Problem." SIAM Conference on Computational Science and Engineering (CSE2021).

\item (\textbf{\color{red}Abstract \& Talk}) \textbf{Gao, Han}, Jianxun Wang, and Luning Sun. ``Suppreresolution and Denoising of Flow Imaging using Physics-Constrained Discrete Learning." SIAM Conference on Computational Science and Engineering (CSE2021).

\item (\textbf{\color{red}Abstract \& Talk}) \textbf{Gao, Han}, Matthew J. Zahr and Jian-Xun Wang. ``A unifying framework of solving forward and inverse problems in fluid mechanics via deep learning." Bulletin of the American Physical Society (2020).

\item (\textbf{\color{red}Poster \& Talk}) \textbf{Gao, Han}, Luning Sun and Jian-Xun Wang. ``PhyGeoNet: Physics-Informed Geometry-Adaptive Convolutional Neural Networks for Solving Parametric PDEs on Irregular Domain." 2020 IMECE NSF Student Poster.

\item (\textbf{\color{red}Poster \& Talk}) \textbf{Gao, Han}, Luning Sun and Jian-Xun Wang. ``PhyGeoNet: Physics-Informed Geometry-Adaptive Convolutional Neural Networks for Solving Parametric PDEs on Irregular Domain." GAMM Juniors’ Summer School on Applied Mathematics and Mechanics -SAMM- (2020) Learning Models from Data: Model Reduction, System Identification and Machine Learning.

\item (\textbf{\color{red}Talk}) \textbf{Gao, Han}, Luning Sun and Jian-Xun Wang. ``Rapid simulator for fluid dynamics based on physics-constrained convolutional neural networks." Virtual minisymposium for SIAM MDS20: Machine Learning for Physical Systems.


\item (\textbf{\color{red}Abstract \& Talk}) \textbf{Gao, Han}, and Jian-Xun Wang. ``A Multi-fidelity Ensemble Kalman Method for Inverse Problems in Cardiovascular Flows." Bulletin of the American Physical Society (2019). 
\item(\textbf{\color{red}Conference Paper \& Talk}) \textbf{Gao, Han}, and Ramesh K. Agarwal. ``Numerical Study of a Hovering Helicopter Rotor Blade in Ground Effect." In AIAA Scitech 2019 Forum, p. 1099. 2019.

\item (\textbf{\color{red}Poster \& Talk}) \textbf{Han Gao}, Xueyu Zhu, Jian-Xun Wang, ``A Bi-fidelity Stochastic Collocation Approach for Uncertainty Quantification in Cardiovascular Modeling", in \textit{Computational Modeling and Image Processing of Biomedical Problems}, (Michigan Technological University, Houghton, Michigan), 15/07/2019 - 15/07/2019 

\item(\textbf{\color{red}Conference Paper \& Talk}) \textbf{Gao, Han}, Quanzhong Liu, Qiulin Qu, and Ramesh K. Agarwal. ``Numerical Study of Round Jet Impingement in Proximity of Ground and a Water Surface." In 2018 Fluid Dynamics Conference, p. 4257. 2018.
\item (\textbf{\color{red}Conference Paper \& Talk}) \textbf{Gao, Han}, Xu Han, Quanzhong Liu, and Ramesh K. Agarwal. ``CFD Simulations of Two Rectangular Water Jets Impinging on a Water Pool." In 2018 Fluid Dynamics Conference, p. 4038. 2018.

\item (\textbf{\color{red}Conference Paper}) Zhang, X., Agarwal, R.K., \textbf{Gao, H}. and Zhou, L., 2020. Numerical Investigation of a Submerged Water Jet Impinging at Various Angles on Ground. In AIAA Scitech 2020 Forum (p. 2038). 

\item (\textbf{\color{red}Abstract}) Wang, J.X., Sun, L., \textbf{Gao, H}. and Pan, S., 2019. Surrogate Modeling for Fluid Flows Using Physics-Constrained, Label-Free Deep Learning. Bulletin of the American Physical Society.
\item (\textbf{\color{red}Conference Paper}) Zhang, Xiang, Ramesh K. Agarwal, \textbf{Han Gao} and Ling Zhou. ``Numerical Simulation of Fountain formation due to Twin-Jet impingement on Ground." In AIAA Aviation 2019 Forum, p. 3643. 2019. 
\item (\textbf{\color{red}Conference Paper}) Liu, Quanzhong, Kefan Xu, \textbf{Han Gao}, and Ramesh K. Agarwal. ``Numerical Simulation of the Cavitation Flow around a Hydrofoil Based on a Coupled CFD-PBM Model." In AIAA Scitech 2019 Forum, p. 2305. 2019. 
\item (\textbf{\color{red}Conference Paper}) Liu, Quanzhong, Lujia Gong, \textbf{Han Gao}, and Ramesh K. Agarwal. ``Numerical Investigation of Cavitation Characteristics of a Liquid Oxygen Turbo Pump." In 2018 Fluid Dynamics Conference, p. 3222. 2018. 
\end{rSection}

\begin{rSection}{Teaching experience}
Partial lecturer (Course design including lecture notes, slides, homework and exam, giving formal lectures, reception of Q\&A, homework, exam grading)
\begin{itemize}
    \item Aerodynamics E37 MEMS 5700 \hfill 2017-2018, WUSTL
\end{itemize}

Teaching assistant (Reception of Q\&A, homework, exam grading and preparing 1 or 2 lectures)
\begin{itemize}
    \item Computational Fluid Dynamics AME 50532 \hfill 2018-2021, ND
    \item Finite Element Methods AME 40541/60541 \hfill 2020-2021, ND
    \item Mechanics II AME 20222 \hfill 2019-2020, ND
    \item Mathematics of Modern Engineering I\& II  ESE 501-502 \hfill 2017-2018, WUSTL
    \item Aeroelasticity \& Flow-Induced Vibrations E37 MEMS 5414 \hfill 2017-2018, WUSTL
\end{itemize}
\end{rSection}

\begin{rSection}{Professional Memberships}
\item American Institute of Aeronautics and Astronautics. Student Membership. Since 2018
\item Society for Industrial and Applied Mathematics. Student Membership. Since 2019
\item The American Physical Society. Student Membership. Since 2019
\end{rSection}

\begin{rSection}{Technical Strengths}
	\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
		Computer Language \ & C++, Python, MATLAB, Jax, Julia \\
		Software \& Tools & Ansys Fluent, OpenFOAM, ICEM, ParaView, Abaqus, Comosol\\
	\end{tabular}
\end{rSection}


\begin{rSection}{Academic Reference}
\begin{itemize}
    \item Jian-Xun Wang (jwang33@nd.edu)
    \item Matthew Zahr (mzahr@nd.edu)
    \item Xueyu Zhu (xueyu-zhu@uiowa.edu)
    \item Shaowu Pan (pans2@rpi.edu)
    \item Ramesh Agarwal (rka@wustl.edu)
\end{itemize}
\end{rSection}


\end{document}
